Visual diagnostics for constrained optimisation with application to guided tours

### 2020-12-09 paper/paper.Rmd
more editing and reference in optim method section

---
title: "Visual diagnostics for constrained optimisation with application to guided tours"
author:
  - name: H.Sherry Zhang
    affiliation: Department of Econometrics and Business Statistics, Monash University 
    email:  Huize.Zhang@monash.edu
abstract: >
  Projection pursuit searches for interesting low-dimensional views of high-dimensional data via the optimisation of an index function. The initial paper by Friedman & Tukey in 1974 stated that  "the  technique  used  for  maximising  the  projection index strongly influences both the statistical and the computational aspects of the procedure." However, while many projection pursuit indices have been proposed in the literature, less work has been done on the optimisation procedures. In this paper we introduce visual diagnostics for optimisation algorithms, in particular those available in the projection pursuit guided tour. These diagnostics and workflows can be applied to a broad class of optimisers, to assess their performance. An R package, ferrn, has been created to implement the diagnostics.
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont, bbm, array, booktabs}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::rjournal_article
---

@@

Visualisation is widely used in exploratory data analysis [@tukey1977exploratory]. Presenting information in a graphical format often allows people to uncover information they would otherwise not be aware of and provides a more comprehensive understanding of the problem at hand. The work presented in this paper combines data visualization with optimization methods. It aims at bring visualization tools into optimization problems to assist users to better understand the performance of their optimization methods in practice. This motivates our work of creating plots to diagnose optimisation algorithms which in turn can be also used not only to understand optimization performance but also to understand and compare the behaviour of different algorithms.

@@

The remainder of the paper is organised as follows. 
Section \ref{optim} provides an overview of optimisation methods, specifically line search methods. 
Section \ref{tour} reviews projection pursuit guided tour, defines the optimisation problem and introduces three existing algorithms.
Section \ref{vis-diag} presents the new visual diagnostics. A data structure is defined to capture information during the optimisation, and used in different types of diagnostic plots.
Section \ref{application} shows applications of how these plots can be used to understand and compare different algorithms. We also discuss how these insights contribute to modifications that improve the algorithms.
Finally, Section \ref{implementation} describes the R package: ferrn, that implements the visual diagnostics.

@@

Our interest is on constrained optimization (REF) as defined in the introduction section and assume that it is not possible to find a solution to the problem in the way of a closed form. That is, the problem consists of finding the minimum or maximum of a function $f \in L^p$ in the constrained $\mathbb{A}$ space.

@@

Optimization methods can be divided in various classes (REF). In this paper, we focused on methods that rely on the objective function derivatives known as gradient methods, and those which are known as derivative free methods where optimization does not rely on the gradient or derivatives information.

@@

Several R implementations address optimization problems with both general purpose as well as tasks specifics solvers. The most prominent one within the general solvers is `optim()` in the package \CRANpkg{stats}[@stats] which have functions for gradient based and derivative free methods. Other packages having similar functionalities include \CRANpkg{nloptr}.

@@

Mathematical details of the geodesic interpolation can be found in @buja2005computational. Figure \ref{fig:tour-path} shows a sketch of the tour path. The blue frames are produced by the projection pursuit optimisation algorithm, and the white frames interpolate between them. The tour method has been implemented in the R package \CRANpkg{tourr} [@tourr], available on the Comprehensive R Archive Network at [https://cran.r-project.org/web/packages/tourr/](https://cran.r-project.org/web/packages/tourr/)

@@

Simulated annealing (`search_better_random`) [@kirkpatrick1983optimization, @bertsimas1993simulated] uses the same sampling process as `search_better` but allows a probabilistic acceptance of a basis with lower index value based on the annealing $T(l)$. Given an initial $T_0$, the temperature at iteration $l$ is defined as $T(l) = \frac{T_0}{\log(l + 1)}$. When a candidate basis fails to have an index value larger than the current basis, simulated annealing gives it a second chance to be accepted with probability $$P= \min\left\{\exp\left[-\frac{\mid I_{\text{cur}} - I_{l} \mid}{T(l)}\right],1\right\}$$ where $I_{(\cdot)}$ denotes the index value of a given basis. This implementation allows the algorithm to jump out of a local maximum and enables a more holistic search of the whole parameter space. This feature is particularly useful when local maxima are present. The algorithm can be written as replacing line 5-8 of Algorithm \ref{random-search} with Algorithm \ref{simulated_annealing}.

@@

The second experiment with the noisy index is to understand how the optimisers perform when a local maximum is present. The dataset used is \\code{boa6} where `x2` and `x7` are informative. The two theoretical best bases are [`r matrix(c(0, 1, 0, 0, 0, 0), nrow = 6)`] and [`r matrix(c(0, 0, 1, 0, 0, 0), nrow = 6)`] with index value `r index <- tourr::norm_kol(nrow(boa6)); proj <- as.matrix(boa6) %*% matrix(c(0, 1, 0, 0, 0, 0), nrow = 6); index(proj)` and `r index <- tourr::norm_kol(nrow(boa6)); proj <- as.matrix(boa6) %*% matrix(c(0, 0, 1, 0, 0, 0), nrow = 6); index(proj)`, respectively. Hence, the global maximum happens when variable `x7` is found. Simulation is done with 20 randomly generated seeds on two optimisers: `search_better` (Figure \ref{fig:kol-better}) and `search_better_random` (Figure \ref{fig:kol-random} and Figure \ref{fig:kol-random-tuned}). Compared to Figure \ref{fig:kol-better} and \ref{fig:kol-random}, Figure \ref{fig:kol-random-tuned}further increases the neighbourhood parameter `alpha` from 0.5 to 0.7 to enlarge the search space.  The data object is collected for each simulation and computation is done to reduce the bases from its original 6D to a 2D points by principal component analysis so as to view the search paths.

@@

In Figure \@ref{fig:kol-random-tuned}, the neighbourhood parameter `alpha` is increased from a 0.5 default to 0.7 to solve the insufficiency of search neighbourhood. Remember that a candidate basis is generated via a linear combination of the current basis and a randomly generated basis on the surface of the sphere, an increase of `alpha` gives more weights on the randomly generated bases and hence allows a wider search. Seed 9982 ((2,4) in Figure \ref{fig:kol-random-tuned}) and seed 2463 ((3,2) in Figure \ref{fig:kol-random-tuned}) benefit from this and find the global maximum.  A noticeable feature of this enlarged search space is that the interpolation paths start to jump around the space but its usefulness is arguable. In seed 2888 (position (3,1)), seed 2986 (position (2,3)), seed 9209 (position (4,4)), just to name a few, this allows a near `V2` bases to switch to a near `V7` bases and as a result these cases find the global maximum. While in the case of seed 6746 (position (1,2)) and seed 2757 (position (1,5)), the jump happens from near `V7` basis to near `V2` basis, it does not come back and leaves those simulations in the local maximum.

@@

The implementation of this projection has been divided into two packages: the data collection object is implemented in the existing `tourr` package while the optimiser diagnostics have been implemented in a new package, `ferrn`. When a guided tour is run, the users can choose if the data from optimisation should be collected via the `verbose` argument. Once the data object has been obtained, the package, `ferrn`, can provide four diagnostic plots as shown in Section \ref{vis-diag}. The structure of package functionality has been listed below.

>>>>

---
title: "Visual diagnostics for constrained optimisation with application to guided tours"
author:
  - name: H.Sherry Zhang
    affiliation: Department of Econometrics and Business Statistics, Monash University 
    email:  Huize.Zhang@monash.edu
abstract: >
  Guided tour searches for interesting low-dimensional views of high-dimensional data via optimising a projection pursuit index function. The first paper of projection pursuit by @friedman1974projection stated that "the  technique used for maximising the projection index strongly influences both the statistical and the computational aspects of the procedure." While many indices have been proposed in the literature, less work has been done on evaluating the performance of the optimisers. In this paper, we implement a data collection object for the optimisation in the guided tour and introduce visual diagnostics based on the data object collected. These diagnostics and workflows can be applied to a broad class of optimisers, to assess their performance. An R package, \pkg{ferrn}, has been created to implement the diagnostics.
preamble: >
  \usepackage{amssymb, amsmath, mathtools, dsfont, bbm, array, booktabs}
  \usepackage[ruled,vlined, linesnumbered]{algorithm2e}
output: rticles::rjournal_article
---

@@

Visualisation is widely used in exploratory data analysis [@tukey1977exploratory; @unwin2015graphical;  @healy2018data; @wilke2019fundamentals]. Presenting information in graphics often unveils information that would otherwise not be aware of and provides a more comprehensive understanding of the problem at hand. The work presented in this paper brings visualization tools into optimisation problems with an aim to better understand the performance of the optimisers in practice. This motivates our work of creating plots to diagnose optimisation algorithms which in turn can be also used not only to understand optimization performance but also to understand and compare the behaviour of different algorithms.

@@

The remainder of the paper is organised as follows. 
Section \ref{optim} provides an overview of optimisation methods, specifically line search methods. 
Section \ref{tour} reviews projection pursuit guided tour, defines the optimisation problem and introduces three existing algorithms.
Section \ref{vis-diag} presents the new visual diagnostics. A data structure is defined to capture information during the optimisation, and used in different types of diagnostic plots.
Section \ref{application} shows applications of how these plots can be used to understand and compare different algorithms. We also discuss how these insights contribute to modifications that improve the algorithms.
Finally, Section \ref{implementation} describes the R package: \pkg{ferrn}, that implements the visual diagnostics.

@@

Our interest is on constrained optimization [@bertsekas2014constrained] as defined in the introduction section and assume that it is not possible to find a solution to the problem in the way of a closed form. That is, the problem consists of finding the minimum or maximum of a function $f \in L^p$ in the constrained $\mathbb{A}$ space.

@@

Optimization methods can be divided in various classes (NOTE: do we want one more sentence on various class: global optim, convex optim, stochastic optim etc?) [@kelley1999iterative; @boyd2004convex; @fletcher2013practical]. In this paper, we focused on methods that rely on the objective function derivatives known as gradient methods, and those which are known as derivative free methods where optimization does not rely on the gradient or derivatives information.

@@

Several R implementations address optimization problems with both general purpose as well as task specifics solvers. The most prominent one within the general solvers is `optim()` in the \CRANpkg{stats} [@stats] package, which have functions for both gradient based and derivative free methods. Another general solver specialised in non-linear optimisation is \CRANpkg{nloptr} [@nloptr]. For more specific optimisation solvers, readers are recommended to svisite the relevant sections in CRAN task review on *optimisation and mathematical programming* [@crantaskreviewoptim].

@@

Mathematical details of the geodesic interpolation can be found in @buja2005computational. Figure \ref{fig:tour-path} shows a sketch of the tour path. The blue frames are produced by the projection pursuit optimisation algorithm, and the white frames interpolate between them. The tour method has been implemented in the R package \CRANpkg{tourr} [@tourr].

@@

Simulated annealing (`search_better_random`) [@kirkpatrick1983optimization; @bertsimas1993simulated] uses the same sampling process as `search_better` but allows a probabilistic acceptance of a basis with lower index value based on the annealing $T(l)$. Given an initial $T_0$, the temperature at iteration $l$ is defined as $T(l) = \frac{T_0}{\log(l + 1)}$. When a candidate basis fails to have an index value larger than the current basis, simulated annealing gives it a second chance to be accepted with probability $$P= \min\left\{\exp\left[-\frac{\mid I_{\text{cur}} - I_{l} \mid}{T(l)}\right],1\right\}$$ where $I_{(\cdot)}$ denotes the index value of a given basis. This implementation allows the algorithm to jump out of a local maximum and enables a more holistic search of the whole parameter space. This feature is particularly useful when local maxima are present. The algorithm can be written as replacing line 5-8 of Algorithm \ref{random-search} with Algorithm \ref{simulated_annealing}.

@@

The second experiment with the noisy index is to understand how the optimisers perform when a local maximum is present. The dataset used is \code{boa6} where `x2` and `x7` are informative. The two theoretical best bases are [`r matrix(c(0, 1, 0, 0, 0, 0), nrow = 6)`] and [`r matrix(c(0, 0, 1, 0, 0, 0), nrow = 6)`] with index value `r index <- tourr::norm_kol(nrow(boa6)); proj <- as.matrix(boa6) %*% matrix(c(0, 1, 0, 0, 0, 0), nrow = 6); index(proj)` and `r index <- tourr::norm_kol(nrow(boa6)); proj <- as.matrix(boa6) %*% matrix(c(0, 0, 1, 0, 0, 0), nrow = 6); index(proj)`, respectively. Hence, the global maximum happens when variable `x7` is found. Simulation is done with 20 randomly generated seeds on two optimisers: `search_better` (Figure \ref{fig:kol-better}) and `search_better_random` (Figure \ref{fig:kol-random} and Figure \ref{fig:kol-random-tuned}). Compared to Figure \ref{fig:kol-better} and \ref{fig:kol-random}, Figure \ref{fig:kol-random-tuned}further increases the neighbourhood parameter `alpha` from 0.5 to 0.7 to enlarge the search space.  The data object is collected for each simulation and computation is done to reduce the bases from its original 6D to a 2D points by principal component analysis so as to view the search paths.

@@

In Figure \ref{fig:kol-random-tuned}, the neighbourhood parameter `alpha` is increased from a 0.5 default to 0.7 to solve the insufficiency of search neighbourhood. Remember that a candidate basis is generated via a linear combination of the current basis and a randomly generated basis on the surface of the sphere, an increase of `alpha` gives more weights on the randomly generated bases and hence allows a wider search. Seed 9982 ((2,4) in Figure \ref{fig:kol-random-tuned}) and seed 2463 ((3,2) in Figure \ref{fig:kol-random-tuned}) benefit from this and find the global maximum.  A noticeable feature of this enlarged search space is that the interpolation paths start to jump around the space but its usefulness is arguable. In seed 2888 (position (3,1)), seed 2986 (position (2,3)), seed 9209 (position (4,4)), just to name a few, this allows a near `V2` bases to switch to a near `V7` bases and as a result these cases find the global maximum. While in the case of seed 6746 (position (1,2)) and seed 2757 (position (1,5)), the jump happens from near `V7` basis to near `V2` basis, it does not come back and leaves those simulations in the local maximum.

@@

The implementation of this projection has been divided into two packages: the data collection object is implemented in the existing CRAN package \CRANpkg{tourr} [@tourr] while the optimiser diagnostics have been implemented in a new package, \pkg{ferrn}. When a guided tour is run, the users can choose if the data from optimisation should be collected via the `verbose` argument. Once the data object has been obtained, the package, \pkg{ferrn}, can provide four diagnostic plots as shown in Section \ref{vis-diag}. The structure of package functionality has been listed below.

### 2020-12-09 paper/paper.tex
more editing and reference in optim method section

\abstract{%
Projection pursuit searches for interesting low-dimensional views of
high-dimensional data via the optimisation of an index function. The
initial paper by Friedman \& Tukey in 1974 stated that ``the technique
used for maximising the projection index strongly influences both the
statistical and the computational aspects of the procedure.'' However,
while many projection pursuit indices have been proposed in the
literature, less work has been done on the optimisation procedures. In
this paper we introduce visual diagnostics for optimisation algorithms,
in particular those available in the projection pursuit guided tour.
These diagnostics and workflows can be applied to a broad class of
optimisers, to assess their performance. An R package, ferrn, has been
created to implement the diagnostics.
}

@@

Visualisation is widely used in exploratory data analysis
\citep{tukey1977exploratory}. Presenting information in a graphical
format often allows people to uncover information they would otherwise
not be aware of and provides a more comprehensive understanding of the
problem at hand. The work presented in this paper combines data
visualization with optimization methods. It aims at bring visualization
tools into optimization problems to assist users to better understand
the performance of their optimization methods in practice. This
motivates our work of creating plots to diagnose optimisation algorithms
which in turn can be also used not only to understand optimization
performance but also to understand and compare the behaviour of
different algorithms.

@@

Our interest is on constrained optimization (REF) as defined in the
introduction section and assume that it is not possible to find a
solution to the problem in the way of a closed form. That is, the
problem consists of finding the minimum or maximum of a function
\(f \in L^p\) in the constrained \(\mathbb{A}\) space.

Optimization methods can be divided in various classes (REF). In this
paper, we focused on methods that rely on the objective function
derivatives known as gradient methods, and those which are known as
derivative free methods where optimization does not rely on the gradient
or derivatives information.

@@

Several R implementations address optimization problems with both
general purpose as well as tasks specifics solvers. The most prominent
one within the general solvers is \texttt{optim()} in the package
\CRANpkg{stats}\citep{stats} which have functions for gradient based and
derivative free methods. Other packages having similar functionalities
include \CRANpkg{nloptr}.

@@

Mathematical details of the geodesic interpolation can be found in
\citet{buja2005computational}. Figure \ref{fig:tour-path} shows a sketch
of the tour path. The blue frames are produced by the projection pursuit
optimisation algorithm, and the white frames interpolate between them.
The tour method has been implemented in the R package \CRANpkg{tourr}
\citep{tourr}, available on the Comprehensive R Archive Network at
\url{https://cran.r-project.org/web/packages/tourr/}

@@

Simulated annealing (\texttt{search\_better\_random})
\citep[\citet{bertsimas1993simulated}]{kirkpatrick1983optimization} uses
the same sampling process as \texttt{search\_better} but allows a
probabilistic acceptance of a basis with lower index value based on the
annealing \(T(l)\). Given an initial \(T_0\), the temperature at
iteration \(l\) is defined as \(T(l) = \frac{T_0}{\log(l + 1)}\). When a
candidate basis fails to have an index value larger than the current
basis, simulated annealing gives it a second chance to be accepted with
probability
\[P= \min\left\{\exp\left[-\frac{\mid I_{\text{cur}} - I_{l} \mid}{T(l)}\right],1\right\}\]
where \(I_{(\cdot)}\) denotes the index value of a given basis. This
implementation allows the algorithm to jump out of a local maximum and
enables a more holistic search of the whole parameter space. This
feature is particularly useful when local maxima are present. The
algorithm can be written as replacing line 5-8 of Algorithm
\ref{random-search} with Algorithm \ref{simulated_annealing}.

@@

The second experiment with the noisy index is to understand how the
optimisers perform when a local maximum is present. The dataset used is
\textbackslash code\{boa6\} where \texttt{x2} and \texttt{x7} are
informative. The two theoretical best bases are {[}0, 1, 0, 0, 0, 0{]}
and {[}0, 0, 1, 0, 0, 0{]} with index value 0.176 and 0.235,
respectively. Hence, the global maximum happens when variable
\texttt{x7} is found. Simulation is done with 20 randomly generated
seeds on two optimisers: \texttt{search\_better} (Figure
\ref{fig:kol-better}) and \texttt{search\_better\_random} (Figure
\ref{fig:kol-random} and Figure \ref{fig:kol-random-tuned}). Compared to
Figure \ref{fig:kol-better} and \ref{fig:kol-random}, Figure
\ref{fig:kol-random-tuned}further increases the neighbourhood parameter
\texttt{alpha} from 0.5 to 0.7 to enlarge the search space. The data
object is collected for each simulation and computation is done to
reduce the bases from its original 6D to a 2D points by principal
component analysis so as to view the search paths.

@@

In Figure @ref\{fig:kol-random-tuned\}, the neighbourhood parameter
\texttt{alpha} is increased from a 0.5 default to 0.7 to solve the
insufficiency of search neighbourhood. Remember that a candidate basis
is generated via a linear combination of the current basis and a
randomly generated basis on the surface of the sphere, an increase of
\texttt{alpha} gives more weights on the randomly generated bases and
hence allows a wider search. Seed 9982 ((2,4) in Figure
\ref{fig:kol-random-tuned}) and seed 2463 ((3,2) in Figure
\ref{fig:kol-random-tuned}) benefit from this and find the global
maximum. A noticeable feature of this enlarged search space is that the
interpolation paths start to jump around the space but its usefulness is
arguable. In seed 2888 (position (3,1)), seed 2986 (position (2,3)),
seed 9209 (position (4,4)), just to name a few, this allows a near
\texttt{V2} bases to switch to a near \texttt{V7} bases and as a result
these cases find the global maximum. While in the case of seed 6746
(position (1,2)) and seed 2757 (position (1,5)), the jump happens from
near \texttt{V7} basis to near \texttt{V2} basis, it does not come back
and leaves those simulations in the local maximum.

@@

The implementation of this projection has been divided into two
packages: the data collection object is implemented in the existing
\texttt{tourr} package while the optimiser diagnostics have been
implemented in a new package, \texttt{ferrn}. When a guided tour is run,
the users can choose if the data from optimisation should be collected
via the \texttt{verbose} argument. Once the data object has been
obtained, the package, \texttt{ferrn}, can provide four diagnostic plots
as shown in Section \ref{vis-diag}. The structure of package
functionality has been listed below.

>>>>

\abstract{%
Guided tour searches for interesting low-dimensional views of
high-dimensional data via optimising a projection pursuit index
function. The first paper of projection pursuit by
\citet{friedman1974projection} stated that ``the technique used for
maximising the projection index strongly influences both the statistical
and the computational aspects of the procedure.'' While many indices
have been proposed in the literature, less work has been done on
evaluating the performance of the optimisers. In this paper, we
implement a data collection object for the optimisation in the guided
tour and introduce visual diagnostics based on the data object
collected. These diagnostics and workflows can be applied to a broad
class of optimisers, to assess their performance. An R package,
\pkg{ferrn}, has been created to implement the diagnostics.
}

@@

Visualisation is widely used in exploratory data analysis
\citep{tukey1977exploratory, unwin2015graphical, healy2018data, wilke2019fundamentals}.
Presenting information in graphics often unveils information that would
otherwise not be aware of and provides a more comprehensive
understanding of the problem at hand. The work presented in this paper
brings visualization tools into optimisation problems with an aim to
better understand the performance of the optimisers in practice. This
motivates our work of creating plots to diagnose optimisation algorithms
which in turn can be also used not only to understand optimization
performance but also to understand and compare the behaviour of
different algorithms.

@@

Our interest is on constrained optimization
\citep{bertsekas2014constrained} as defined in the introduction section
and assume that it is not possible to find a solution to the problem in
the way of a closed form. That is, the problem consists of finding the
minimum or maximum of a function \(f \in L^p\) in the constrained
\(\mathbb{A}\) space.

Optimization methods can be divided in various classes (NOTE: do we want
one more sentence on various class: global optim, convex optim,
stochastic optim etc?)
\citep{kelley1999iterative, boyd2004convex, fletcher2013practical}. In
this paper, we focused on methods that rely on the objective function
derivatives known as gradient methods, and those which are known as
derivative free methods where optimization does not rely on the gradient
or derivatives information.

@@

Several R implementations address optimization problems with both
general purpose as well as task specifics solvers. The most prominent
one within the general solvers is \texttt{optim()} in the
\CRANpkg{stats} \citep{stats} package, which have functions for both
gradient based and derivative free methods. Another general solver
specialised in non-linear optimisation is \CRANpkg{nloptr}
\citep{nloptr}. For more specific optimisation solvers, readers are
recommended to svisite the relevant sections in CRAN task review on
\emph{optimisation and mathematical programming}
\citep{crantaskreviewoptim}.

@@

Mathematical details of the geodesic interpolation can be found in
\citet{buja2005computational}. Figure \ref{fig:tour-path} shows a sketch
of the tour path. The blue frames are produced by the projection pursuit
optimisation algorithm, and the white frames interpolate between them.
The tour method has been implemented in the R package \CRANpkg{tourr}
\citep{tourr}.

@@

Simulated annealing (\texttt{search\_better\_random})
\citep{kirkpatrick1983optimization, bertsimas1993simulated} uses the
same sampling process as \texttt{search\_better} but allows a
probabilistic acceptance of a basis with lower index value based on the
annealing \(T(l)\). Given an initial \(T_0\), the temperature at
iteration \(l\) is defined as \(T(l) = \frac{T_0}{\log(l + 1)}\). When a
candidate basis fails to have an index value larger than the current
basis, simulated annealing gives it a second chance to be accepted with
probability
\[P= \min\left\{\exp\left[-\frac{\mid I_{\text{cur}} - I_{l} \mid}{T(l)}\right],1\right\}\]
where \(I_{(\cdot)}\) denotes the index value of a given basis. This
implementation allows the algorithm to jump out of a local maximum and
enables a more holistic search of the whole parameter space. This
feature is particularly useful when local maxima are present. The
algorithm can be written as replacing line 5-8 of Algorithm
\ref{random-search} with Algorithm \ref{simulated_annealing}.

@@

The second experiment with the noisy index is to understand how the
optimisers perform when a local maximum is present. The dataset used is
\code{boa6} where \texttt{x2} and \texttt{x7} are informative. The two
theoretical best bases are {[}0, 1, 0, 0, 0, 0{]} and {[}0, 0, 1, 0, 0,
0{]} with index value 0.176 and 0.235, respectively. Hence, the global
maximum happens when variable \texttt{x7} is found. Simulation is done
with 20 randomly generated seeds on two optimisers:
\texttt{search\_better} (Figure \ref{fig:kol-better}) and
\texttt{search\_better\_random} (Figure \ref{fig:kol-random} and Figure
\ref{fig:kol-random-tuned}). Compared to Figure \ref{fig:kol-better} and
\ref{fig:kol-random}, Figure \ref{fig:kol-random-tuned}further increases
the neighbourhood parameter \texttt{alpha} from 0.5 to 0.7 to enlarge
the search space. The data object is collected for each simulation and
computation is done to reduce the bases from its original 6D to a 2D
points by principal component analysis so as to view the search paths.

@@

In Figure \ref{fig:kol-random-tuned}, the neighbourhood parameter
\texttt{alpha} is increased from a 0.5 default to 0.7 to solve the
insufficiency of search neighbourhood. Remember that a candidate basis
is generated via a linear combination of the current basis and a
randomly generated basis on the surface of the sphere, an increase of
\texttt{alpha} gives more weights on the randomly generated bases and
hence allows a wider search. Seed 9982 ((2,4) in Figure
\ref{fig:kol-random-tuned}) and seed 2463 ((3,2) in Figure
\ref{fig:kol-random-tuned}) benefit from this and find the global
maximum. A noticeable feature of this enlarged search space is that the
interpolation paths start to jump around the space but its usefulness is
arguable. In seed 2888 (position (3,1)), seed 2986 (position (2,3)),
seed 9209 (position (4,4)), just to name a few, this allows a near
\texttt{V2} bases to switch to a near \texttt{V7} bases and as a result
these cases find the global maximum. While in the case of seed 6746
(position (1,2)) and seed 2757 (position (1,5)), the jump happens from
near \texttt{V7} basis to near \texttt{V2} basis, it does not come back
and leaves those simulations in the local maximum.

@@

The implementation of this projection has been divided into two
packages: the data collection object is implemented in the existing CRAN
package \CRANpkg{tourr} \citep{tourr} while the optimiser diagnostics
have been implemented in a new package, \pkg{ferrn}. When a guided tour
is run, the users can choose if the data from optimisation should be
collected via the \texttt{verbose} argument. Once the data object has
been obtained, the package, \pkg{ferrn}, can provide four diagnostic
plots as shown in Section \ref{vis-diag}. The structure of package
functionality has been listed below.
